\noindent
\textbf{Columbia University.} 
Seok maintains a 600 sq-ft laboratory with 11 stations for designing VLSI hardware, and 5 stations for testing VLSI hardware. 
The available instruments include a high-precision current-meters, desktop multi-meter, five workstations equipped with National Instrument (NI) Labview digital/analog acquisition/actuation boards, programmable -40/+140$^oC$ environmental chambers, a professional soldering station and multiple programmable power supplies. 
Seok has accesses to a variety of software including NI Academic Site License for automated testing; industrial EDA tools such as H-SPICE, DesignCompiler, PrimeTime. %which include Synopsis H-SPICE, DesignCompiler, PowerCompiler, PrimeTime, PrimePower, Mentor-Graphics Eldo, Calibre, Cadence Virtuoso, Spectre, Encounter/Velocity, ELC; the nanometer VLSI technology design kits from 180nm down to 28nm nodes; and standard core cell, IO cells, and bonding pad libraries for most of those technologies for design automation. 
%Seok maintains 7 high performance Linux computing servers (each server has 4 to 24 cores and 16-32GB RAM), 9 Linux/Windows workstations, and an 8TB file-server. 

\vspace{3pt}
\noindent
\textbf{University of Illinois.}
Kim, Hanumolu, and Hwu are affiliated with Coordinated Science Laboratory. 
They all have access to cluster computing facilities to run parallel simulations. 
%maintains a cluster of 12 Intel Xeon-based dual-socket servers and a cluster of 24 AMD APU-based single-socket servers, 
%connected by a stack of high-speed Ethernet switches linked to the campus network backbone with a 100Gb/s uplink to the CSL facility protected behind the campus firewall.
Kim requests two servers to strengthen the cluster as some old servers need to be retired. 
%These two clusters provide more than 300 CPU cores, facilitating fast exploration of various system architectures, simulation of a system designed at the register-transfer and gate levels, and physical design of chips for the project.
%The hardware lab at the University of Illinois is a characterization facility that consists of 
They also maintain computer-controlled instrumentation tools including DC to RF cascade probe stations, device characterization equipment, 
mixed-signal circuit characterization equipment (RF signal sources, data acquisition, arbitrary waveform generators, etc.), RF devices and circuit characterization equipment, 
%(26 GHz spectrum analyzer, 20 GHz network analyzer), 
and communications test equipment capable of generating almost all digital baseband and RF modulation schemes and performing bit-error-rate and communication channel measurements up to 26GHz. 
%Kim, Hanumolu, and Hwu have accesses to the state-of-the-art circuit design, analysis, and synthesis tools from Cadence and Synopsys.

\vspace{3pt}
\noindent
\textbf{University of Southern California.}
Annavaram has a simulation pool server rack consisting of about 50 servers (200 cores and about 4GB of memory per core). 
%The server pool is fully configured for auto job scheduling and remote management. 
%The proposed work will use and develop a variety of software simulation tools which will be simulated on the pool. 
Annavaram requests two servers to strengthen the pool as some old servers need to be retired. %due to their age. 
The lab currently hosts a set of Xilinx ML-509 FPGA boards that use the Virtex-5 FPGAs which may be used to design and debug the core. 
%He has also access to a separate cluster of compute nodes that can run all Xilinx design tools. 
